# Systematic review extraction parsing

- [x] authors: nothing
- [x] study_id: nothing
- [x] contextualization: comment (nothing)
- [x] follow_up_actions: comment (nothing)
- [x] missing_data_handling: comment (nothing)
- [x] notes: nothing
- [x] clustering_features: none
- [x] other_features: none

- [x] year: histogram demonstrating frequency of mTBI subtyping studies
- [x] concussion_definition: heatmap of different criteria of mTBI/concussion definition used
- [x] population: bar chart of populations examined
- [x] age: linerange plot of ages examined
- [x] n_male: include in histogram above
- [x] n_female: include in histogram above
- [x] n: histogram of sample sizes examined
- [x] race_ethnicity: heatmap
- [x] time_post_injury: complex figure 1
- [x] clustering_method: bar chart (easy?)
- [x] validation_method: bar chart (easy)
- [x] summary: complex figure 2 (tough)


## Importing extraction, helper functions

```{r}
# {{{
library(jsonlite)
library(ggplot2)
library(dplyr)
library(stringr)
library(ComplexHeatmap)
library(circlize)
library(viridis)

data <- fromJSON("../extraction.json")

fig_path <- function(path) {
    return(paste0("figures/", format(Sys.Date(), "%Y_%m_%d"), "_", path, ".png"))
}

# }}}
```

## Study summary

```{r}
tibble(# {{{
    Study = data$"clean_name",
    "Population type" = data$"population",
    N = data$"n",
    "Clustering method" = data$"clustering_method",
    "Validation method" = "",
    "Time post-injury" = data$"time_post_injury",
    "Identified clusters" = ""
) |>
    knitr::kable(format = "markdown")

for (name in names(data)) {
    print(name)
}# }}}
```

### Missing data

```{r}
# {{{
table(data$"missing_data_handling")
# }}}
```


## Year

```{r}
# {{{
year_histogram <-data.frame(data$"year") |>
    ggplot(aes(x = data.year)) +
    geom_histogram(
        binwidth = 1,
        fill = "gray",
        colour = "black"
    ) + 
    coord_cartesian(xlim = c(1995, 2025)) +
    scale_y_continuous(
        breaks = 1:6,
        minor_breaks = NULL
    ) +
    scale_x_continuous(
        breaks = c(unique(data$"year")),
        minor_breaks = NULL,
        expand = expansion(mult = c(0.02, 0.02))
    ) +
    labs(x = "Year of publication", y = "Number of studies") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(
    fig_path("year_histogram.png"),
    year_histogram,
    width = 6,
    height = 3,
    dpi = 300
)
# }}}
```

### Concussion definition

```{r}
# {{{

library(ComplexHeatmap)
library(circlize)
concussion_df <- data$"concussion_definition"
rownames(concussion_df) <- data$"clean_name"
clustered_df <- concussion_df |>
    dplyr::mutate(
        at_least_one_symptom = dplyr::case_when(
            at_least_one_symptom  == "NR" ~ 0,
            at_least_one_symptom  == "Yes" ~ 1,
            TRUE ~ NA
        ),
        altered_mental_state = dplyr::case_when(
            altered_mental_state  == "NR" ~ 0,
            altered_mental_state  == "<= 30 minutes" ~ 1,
            altered_mental_state  == "<= 24 hours" ~ 2,
            altered_mental_state  == "Any" ~ 3,
            TRUE ~ NA
        ),
        focal_neurological_signs = dplyr::case_when(
            focal_neurological_signs == "NR" ~ 0,
            focal_neurological_signs == "Transient" ~ 1,
            focal_neurological_signs == "Any" ~ 2,
            TRUE ~ NA
        ),
        gcs = dplyr::case_when(
            gcs == "NR" ~ 0,
            gcs == ">= 14" ~ 1,
            gcs == ">= 13" ~ 2,
            TRUE ~ NA
        ),
        hospitalization_time_less_24 = dplyr::case_when(
            hospitalization_time_less_24 == "NR" ~ 0,
            hospitalization_time_less_24 == "<= 24 hours" ~ 1,
            TRUE ~ NA
        ),
        impaired_balance_less_24 = dplyr::case_when(
            impaired_balance_less_24 == "NR" ~ 0,
            impaired_balance_less_24 == "Yes" ~ 1,
            TRUE ~ NA
        ),
        impaired_learning_and_memory_less_48 = dplyr::case_when(
            impaired_learning_and_memory_less_48 == "NR" ~ 0,
            impaired_learning_and_memory_less_48 == "Yes" ~ 1,
            TRUE ~ NA
        ),
        loc = dplyr::case_when(
            loc == "NR" ~ 0,
            loc == "<= 30 minutes" ~ 1,
            loc == "Any" ~ 2,
            TRUE ~ NA
        ),
        normal_imaging = dplyr::case_when(
            normal_imaging == "NR" ~ 0,
            normal_imaging == "Yes" ~ 1,
            TRUE ~ NA
        ),
        post_traumatic_amnesia = dplyr::case_when(
            post_traumatic_amnesia == "NR" ~ 0,
            post_traumatic_amnesia == "<= 24 hours" ~ 1,
            post_traumatic_amnesia == "Any" ~ 2,
            TRUE ~ NA
        ),
        reduced_reaction_less_48 = dplyr::case_when(
            reduced_reaction_less_48 == "NR" ~ 0,
            reduced_reaction_less_48 == "Yes" ~ 2,
            TRUE ~ NA
        ),
        restricted_activity_more_5 = dplyr::case_when(
            restricted_activity_more_5 == "NR" ~ 0,
            restricted_activity_more_5 == "Yes" ~ 1,
            TRUE ~ NA
        ),
        other_algorithm = dplyr::case_when(
            other_algorithm == "NR" ~ 0,
            other_algorithm == "Yes" ~ 1,
            TRUE ~ NA
        ),
        diagnosis = dplyr::case_when(
            diagnosis == "NR" ~ 0,
            diagnosis == "Yes" ~ 1,
            TRUE ~ NA
        )
    )
ht <- draw(Heatmap(as.matrix(clustered_df)))
roword <- rownames(clustered_df)[row_order(ht)]
colord <- colnames(clustered_df)[column_order(ht)]
neat_names <- c(
    "At least one symptom",
    "Altered mental state",
    "Focal neurological signs",
    "Glasgow Coma Scale",
    "Hospitalization less than 24h",
    "Impaired balance less than 24h",
    "Impaired learning and memory",
    "Loss of consciousness",
    "Normal structural imaging",
    "Post-traumatic amnesia",
    "Reduced reaction time",
    "Restricted activity more than 5d",
    "Other algorithm",
    "Diagnosis"
)
colour_schemes <- list(
    "At least one symptom"              =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Altered mental state"              =  c("NR"  =  "white" , "Any"            =  "lightblue4"   , "<= 30 minutes"  =  "palegreen"   , "<= 24 hours"  =  "royalblue") ,
    "Focal neurological signs"          =  c("NR"  =  "white" , "Any"            =  "deeppink"     , "Transient"      =  "cyan4")      ,
    "Glasgow Coma Scale"                =  c("NR"  =  "white" , ">= 14"          =  "palegreen4"   , ">= 13"          =  "lightblue4") ,
    "Hospitalization less than 24h"     =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Impaired balance less than 24h"    =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Impaired learning and memory"      =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Loss of consciousness"             =  c("NR"  =  "white" , "<= 30 minutes"  =  "lightblue4"   , "Any"            =  "deeppink")   ,
    "Normal structural imaging"         =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Post-traumatic amnesia"            =  c("NR"  =  "white" , "<= 24 hours"    =  "lightblue4"   , "Any"            =  "deeppink")   ,
    "Reduced reaction time"             =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Restricted activity more than 5d"  =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Other algorithm"                   =  c("NR"  =  "white" , "Yes"            =  "darkorchid2") ,
    "Diagnosis"                         =  c("NR"  =  "white" , "Yes"            =  "darkorchid2")
)
heatmap_row_order <- c(
    "Hanlon 1999",
    "Maestas 2014",
    "Snell 2015",
    "Thaler 2013",
    "Blundell 2025",
    "Cicerone 1995",
    "Bailie 2016",
    "Anderson 2025",
    "Bui 2022",
    "Kinney 2024",
    "Ingram 2023",
    "Pugh 2019",
    "Rakers 2021",
    "Fino 2022",
    "Armañanzas 2024",
    "Macgregor 2024",
    "Lyons 2022",
    "Yeates 2019",
    "Chan 2003",
    "Gumus 2022",
    "Garcia 2022",
    "Si 2018a",
    "Si 2018b",
    "Hicks 2022",
    "Maietta 2022",
    "Rabinowitz 2013",
    "Ransom 2016",
    "Rosenblatt 2021",
    "Simons 2024",
    "Visscher 2019"
)
concussion_df[concussion_df == "NR"] <- NA
hms <- lapply(
    seq_len(ncol(concussion_df)),
    function(i) {
        mat <- matrix(concussion_df[, i])
        rownames(mat) <- rownames(concussion_df)
        colnames(mat) <- neat_names[i]
        mat <- mat[heatmap_row_order, , drop = FALSE]
        legend <- FALSE
        # Column 12's legend is used as a placeholder for all binary 
        # columns.
        if (i %in% c(2, 4, 10, 8, 3, 14)) {
            legend <- TRUE
        }
        if (i == 14) {
            mat_name <- "Other"
        } else {
            mat_name <- neat_names[i]
        }
        Heatmap(
            mat,
            name = mat_name,
            row_names_side = "left",
            na_col = "white",
            col = colour_schemes[[i]],
            rect_gp = gpar(col = "black", lwd = 1),
            show_heatmap_legend = legend,
            column_names_rot = 45
        )
    }
)
names(hms) <- colnames(concussion_df)
heatmap_order <- c(
    "altered_mental_state",
    "gcs",
    "post_traumatic_amnesia",
    "loc",
    "focal_neurological_signs",
    "at_least_one_symptom",
    "normal_imaging",
    "hospitalization_time_less_24",
    "impaired_balance_less_24",
    "impaired_learning_and_memory_less_48",
    "reduced_reaction_less_48",
    "restricted_activity_more_5",
    "surgery_not_needed",
    "other_algorithm",
    "diagnosis"
)
hms <- hms[heatmap_order]
ht <- Reduce(`+`, hms)
draw(ht, ht_gap = unit(0, "mm"))

pdf("figures/2026_04_01_concussion_definition.pdf", width = 9, height = 8)
draw(
  ht,
  ht_gap = unit(0, "mm")
)
dev.off()

# }}}
```

### Population

```{r}
# {{{
pop_df <- data.frame(
    population = str_to_sentence(data$"population")
)
pop_df$"population" <- gsub(" and ", " and \n", pop_df$"population")
pop_plot <- pop_df |>
    ggplot(
        aes(x = reorder(population, population, FUN = length, decreasing = TRUE))
    ) +
    geom_bar() +
    scale_y_continuous(
        breaks = 0:18,
        minor_breaks = NULL
    ) +
    labs(x = "Population examined", y = "Number of studies") +
    theme_bw() +
    theme(
        text = element_text(size = 12)
    )
ggsave(
    fig_path("pop_plot"),
    pop_plot,
    width = 5,
    height = 4,
    dpi = 300
)
# }}}
```

### Age

```{r}
# {{{
age_df <- data$"age" |>
    mutate(author = data$"clean_name")
age_df[age_df == "not reported"] <- NA
age_df[, 1:4] <- data.frame(apply(age_df[, 1:4], 2, function(x) as.numeric(x)))
age_df$"sd_low" <- age_df$"mean" - age_df$"sd"
age_df$"sd_high" <- age_df$"mean" + age_df$"sd"
age_df <- arrange(age_df, mean)
age_df$"author" <- factor(age_df$"author", levels = age_df$"author")
age_df <- age_df |>
    filter(!author %in% c("Bui 2022", "Si 2018b"))
age_plot <- age_df |>
    ggplot(aes(x = author)) +
    geom_linerange(aes(ymin = minimum, ymax = maximum, colour = "Range"), linewidth = 2, alpha = 0.6) +
    geom_linerange(aes(ymin = sd_low, ymax = sd_high, colour = "Standard deviation"), linewidth = 1) +
    geom_point(aes(y = mean, colour = "Mean"), size = 2.5, alpha = 0.3) +
    geom_hline(yintercept = 18) +
    coord_flip() +
    ylab("Age of sample (years)") +
    xlab(NULL) +
    scale_colour_manual(
        name = "Statistics",
        values = c("Mean" = "black", "Standard deviation" = "dodgerblue", "Range" = "darkorange")
    ) +
    scale_y_continuous(
        limits = c(0, 95),
        breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95),
        minor_breaks = NULL,
        expand = expansion(mult = c(0, 0.01))
    ) +
    theme_bw()
age_plot
ggsave(
    fig_path("age_plot"),
    age_plot,
    width = 8,
    height = 5,
    dpi = 300
)
# }}}
```

### n

```{r}
# {{{
n_df <- data.frame(
    n = c(data$"n", data$"n_female", data$"n_male"),
    Sex = c(rep("All", 30), rep("F", 30), rep("M", 30))
)
n_df[n_df == 0] <- 1

x <- data |>
    dplyr::mutate(prop_female = 100 * n_female / n) |>
    pull(prop_female)
median(x, na.rm = TRUE)
quantile(x, probs = c(0.25, 0.75), na.rm = TRUE)
# 32 [19, 42]

my_scale <- scale_x_continuous(
    trans = "log10",
    breaks = c(1, 10, 100, 1000, 10000, 100000),
    minor_breaks = NULL,
    labels = c("0", "10", "100", "1000", "10000", "100000")
)
n_plot <- n_df |>
    ggplot(aes(x = n, fill = Sex, colour = Sex)) +
    geom_histogram(
        alpha = 0.3,
        bins = 25
    ) +
    expand_limits(x = 50) +
    my_scale +
    scale_y_continuous(
        breaks = 1:7,
        minor_breaks = NULL,
        expand = expansion(mult = c(0, 0.1))
    ) +
    labs(x = "Size of clustered sample", y = "Number of studies") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    theme(text = element_text(size = 14)) +
    facet_wrap(~ Sex, nrow = 1)
n_plot

ggsave(
    fig_path("n_plot"),
    n_plot,
    width = 8,
    height = 3.5,
    dpi = 300
)
# }}}
```

### Race

```{r}
# {{{
library(circlize)
race_mat <- as.matrix(data$"race")
rownames(race_mat) <- data$"clean_name"
colnames(race_mat) <- c(
    "American Indian\n+ Alaskan Native",
    "Asian",
    "Black\n+ African Ancestry",
    "Hispanic",
    "Native Hawaiian\n+ Pacific Islander",
    "New Zealand\nMaori",
    "Unknown\n+ Other",
    "White\n+ European"
)
# account for NAs
race_mat[race_mat == "NR"] <- NA
# convert values to numeric
race_mat <- apply(
    race_mat,
    2,
    function(x) {
        as.numeric(x)
    }
)
# convert values to % distribution by study
race_mat <- race_mat / rowSums(race_mat, na.rm = TRUE)
race_mat <- race_mat * 100
# order columns by prevalence (barring unknown/other)
cols <- names(sort(-colSums(race_mat, na.rm = TRUE)))
cols <- c(cols[-1], cols[1])
col_fun <- colorRamp2(c(0, 100), c("red", "royalblue"))
rownames(race_mat) <- data$"clean_name"
race_mat <- race_mat[order(-apply(race_mat, 1, function(x) sum(!is.na(x)))), order(-apply(race_mat, 2, function(x) sum(!is.na(x))))]
race_mat <- t(race_mat)
race_hm <- Heatmap(
    race_mat,
    name = "Proportion\nof\nsample\n",
    na_col = "white",
    rect_gp = gpar(col = "black", lwd = 1),
    col = col_fun,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    row_names_side = "left",
    show_column_names = TRUE
)
race_hm

pdf("figures/2026_04_01_race_hm.pdf", width = 9, height = 5)
draw(race_hm)
dev.off()
# }}}
```

### Time post-injury

```{r}
# {{{
print(paste0(1:30, ". ", data$"clean_name", ": ", data$"time_post_injury"))
#1. Anderson 2025: 10 w
#    - mean point? at 10 weeks
#2. Armañanzas 2024: less than 120 h, median 50.03 h, iqr 27.20 h to 70.47 h
#    - median point at 50.03 h
#    - criteria max 120 h
#3. Bailie 2016: less than 2 years
#    - criteria max 2 years
#4. Blundell 2025: daily from mean 6.63 to mean 41.63, sd 8.12
#    - collection band from 6.63 to 41.63 h
#    - sd band from 6.63-8.12 to 41.63+8.12
#5. Bui 2022: A pre-injury time point of unspecified time, once below 6 hours, from the 24-48 hour post-injury time point, once at asymptomatic, once at unrestricted rtp, once 7 days post-rtp, once 6 months post-rtp
#6. Chan 2003: between 3 and 78 months post-injury, median 12 months
#    - median point at 12 m
#    - range band from 3 m to 78 m
#7. Cicerone 1995: at least 3 months post-injury, range of 3 to 52 months post-injury, mean of 13.9 months and SD of 11.8 months 
#    - criteria min 3 m
#    - range band 3 m to 52 m
#    - mean point at 13.9 m
#    - sd band of 11.8 m
#8. Fino 2022: 9.2 (7.9) years. Based on lifetime history of veterans so the range is wide.
#    - mean point at 9.2 y
#    - sd band at 7.9 y
#9. Gumus 2022: Between 3 months and an unspecified number of years
#10. Hanlon 1999: median of 177 days, range of 3-40 months
#11. Hicks 2022: mean of 4 days, SD of 4 days
#12. Ingram 2023: 61.6 (51.8) months
#13. Kinney 2024: not reported
#14. Lyons 2022: 28 days post-injury
#15. Macgregor 2024: 24 months
#16. Maestas 2014: 2-weeks post-injury.
#17. Maietta 2022: 72 hrs AND 4-7 days AND 8-30 days
#18. Pugh 2019: not reported
#19. Rabinowitz 2013: less than 48 hours
#20. Rakers 2021: 2 weeks and 3 months and 6 months post-injury
#21. Ransom 2016: less than 4 weeks of injury, median of 16 days, range of 7 to 28 days
#23. Simons 2024: less than 12 hours post-injury
#24. Snell 2015: less than 3 months was the criteria, with actual mean of 40.8 days and SD of 23.4 days
#25. Thaler 2013: Average of 49.5 (SD 25.4) months post-injury
#26. Visscher 2019: median of 52 days post-injury, IQR of 140 days
#27. Yeates 2019: 0-48 hours
anderson_df <- data.frame(study = "Anderson 2025", mean_time = 10 * 7)
armananzas_df <- data.frame(study = "Armañanzas 2024", median_time = 50.3 / 24, criteria_max = 120 / 24)
bailie_df <- data.frame(study = "Bailie 2016", criteria_max = 2 * 365)
blundell_df <- data.frame(study = "Blundell 2025", continuous_start = 6.63, continuous_end = 41.63, mean_time = 24.13, sd = 8.12)
# Bui not included due to timeline being based on unspecified RTP time
chan_df <- data.frame(study = "Chan 2003", median_time = 12*30, min_time = 3 * 30, max_time = 78 * 30)
#cicerone_df <- data.frame(study = "Cicerone 1995", criteria_min = 3 * 30, min_time = 3 * 30, max_time = 52 * 30, mean_time = 13.9 * 30, sd = 11.8 * 30)
cicerone_df <- data.frame(study = "Cicerone 1995", min_time = 3 * 30, max_time = 52 * 30, mean_time = 13.9 * 30, sd = 11.8 * 30)
fino_df <- data.frame(study = "Fino 2022", mean_time = 9.2 * 365, sd = 7.9 * 365)
garcia_df1 <- data.frame(study = "Garcia 2022 (1)", mean_time = 6.51/24)
garcia_df2 <- data.frame(study = "Garcia 2022 (2)", mean_time = 6.51/24)
garcia_df3 <- data.frame(study = "Garcia 2022 (3)", criteria_min = 1, criteria_max = 2)
garcia_df4 <- data.frame(study = "Garcia 2022 (4)", criteria_min = 1, criteria_max = 2)
gumus_df <- data.frame(study = "Gumus 2022", criteria_min = 3 * 30)
hanlon_df <- data.frame(study = "Hanlon 1999", median_time = 177, min_time = 3*30, max_time = 40*30)
hicks_df <- data.frame(study = "Hicks 2022", mean_time = 4, sd = 4)
ingram_df <- data.frame(study = "Ingram 2023", mean_time = 61.6*30, sd = 51.8*30, min_time = 0.3*30, max_time = 360*30)
lyons_df <- data.frame(study = "Lyons 2022", mean_time = 28)
macgregor_df <- data.frame(study = "Macgregor 2024", mean_time = 24*30)
maestas_df <- data.frame(study = "Maestas 2014", criteria_max = 2 * 7)
maietta_df1 <- data.frame(study = "Maietta 2022 (1)", mean_time = 72 / 24)
maietta_df2 <- data.frame(study = "Maietta 2022 (2)", min_time = 4, max_time = 7)
maietta_df3 <- data.frame(study = "Maietta 2022 (3)", min_time = 8, max_time = 30)
rabinowitz_df <- data.frame(study = "Rabinowitz 2013", mean_time = 7.2, sd = 10.8, min_time = 0.5, max_time = 210)
rakers_df <- data.frame(study = "Rakers 2021", continuous_start = 2 * 7, continuous_end = 6 * 30)
#ransom_df <- data.frame(study = "Ransom 2016", median_time = 16, min_time = 7, max_time = 28, criteria_max = 28)
ransom_df <- data.frame(study = "Ransom 2016", median_time = 16, min_time = 7, max_time = 28)
si2018a_df <- data.frame(study = "Si 2018a", mean_time = 1)
si2018b_df <- data.frame(study = "Si 2018b", mean_time = 1)
simon_df <- data.frame(study = "Simons 2024", criteria_max = 12 / 24)
snell_df <- data.frame(study = "Snell 2015", criteria_max = 3 * 30, mean_time = 40.8, sd = 23.4)
thaler_df <- data.frame(study = "Thaler 2013", mean_time = 49.5 * 30, sd = 25.4 * 30)
visscher_df <- data.frame(study = "Visscher 2019", median_time = 52)
yeates_df <- data.frame(study = "Yeates 2019", criteria_max = 48 / 24)
timeline_data <- dplyr::bind_rows(
    anderson_df,
    armananzas_df,
    bailie_df,
    blundell_df,
    chan_df,
    cicerone_df,
    fino_df,
    garcia_df1,
    garcia_df2,
    garcia_df3,
    garcia_df4,
    gumus_df,
    hanlon_df,
    hicks_df,
    ingram_df,
    lyons_df,
    macgregor_df,
    maestas_df,
    maietta_df1,
    maietta_df2,
    maietta_df3,
    rabinowitz_df,
    rakers_df,
    ransom_df,
    si2018a_df,
    si2018b_df,
    simon_df,
    snell_df,
    thaler_df,
    visscher_df,
    yeates_df
)
timeline_data$"sd_low" <- timeline_data$"mean_time" - timeline_data$"sd"
timeline_data$"sd_high" <- timeline_data$"mean_time" + timeline_data$"sd"
timeline_data$"sd_low"[timeline_data$"sd_low" <= 0] <- 0.25
timeline_data$"min_val" <- timeline_data[, 2:ncol(timeline_data)] |>
    apply(1, min, na.rm = TRUE)
timeline_data <- arrange(timeline_data, -min_val)
timeline_data$study <- factor(timeline_data$study, levels = unique(timeline_data$study))
timeline_data$study_num <- as.numeric(timeline_data$study)
recruitment_line_height <- 0.5
timeline_plot <- timeline_data |>
    ggplot(aes(y = study_num)) +
    geom_errorbar(
        aes(
            xmin = min_time,
            xmax = max_time,
            color = "Range"
        ),
        width = 0,
        alpha = 0.5,
        linewidth = 8
    ) +
    geom_errorbar(
        data = timeline_data |> filter(!is.na(sd)),
        aes(
            xmin = sd_low,
            xmax = sd_high,
            color = "SD (±1)"
        ),
        width = 0,
        alpha = 0.5,
        linewidth = 6
    ) +
    geom_errorbar(
        aes(
            xmin = continuous_start,
            xmax = continuous_end,
            color = "Multiple time points"
        ),
        width = 0,
        alpha = 0.5,
        linewidth = 4
    ) +
    geom_point(
        data = timeline_data |> filter(!is.na(mean_time)),
        aes(x = mean_time, shape = "Mean / single point"), 
        color = "purple",
        alpha = 1,
        size = 4
    ) +
    geom_point(
        data = timeline_data |> filter(!is.na(median_time)),
        aes(x = median_time, shape = "Median"), 
        color = "forestgreen",
        alpha = 1,
        size = 5
    ) +
    scale_shape_manual(
        name = "",
        values = c("Mean / single point" = 16, "Median" = 18)
    ) +
    scale_color_manual(
        name = "",
        values = c(
            "Range" = "skyblue",
            "SD (±1)" = "darkorange",
            "Multiple time points" = "darkseagreen"
        )
    ) +
    scale_linetype_manual(
        name = "",
        values = c("Recruitment min." = "solid", "Recruitment max." = "solid"),
        breaks = c("Recruitment min.", "Recruitment max."),
        guide = guide_legend(override.aes = list(linewidth = 0.8))
    ) +
    labs(
        title = "Time since last injury of clustered sample",
        x = "Time",
        y = "Study"
    ) +
    scale_x_continuous(
        trans = "log10",
        limits = c(0.25, 40000),
        breaks = c(0.25, 0.5, 1:7, 14, 30*(1:6), 365*(1:5), 3653 , 50*365),
        labels = c("<= 6h" , "12h" , paste0(1:7 , "d") , "14d", paste0(1:6, "m"), paste0(1:5, "y"), "10y"   , "50y") ,
        minor_breaks = NULL,
        expand = c(0, 0)
    ) +
    scale_y_continuous(
        breaks = 1:length(timeline_data$"study"),
        labels = timeline_data$"study",
        minor_breaks = NULL,
        expand = c(0.02, 0)
    ) +
    geom_linerange(
        data = timeline_data |> filter(!is.na(criteria_min)),
        aes(
            x = criteria_min,
            ymin = study_num - recruitment_line_height + 0.05,
            ymax = study_num + recruitment_line_height - 0.05,
            linetype = "Recruitment min."
        ),
        color = "blue",
        linewidth = 2
    ) +
    geom_linerange(
        data = timeline_data |> filter(!is.na(criteria_max)),
        aes(
            x = criteria_max,
            ymin = study_num - recruitment_line_height + 0.05,
            ymax = study_num + recruitment_line_height - 0.05,
            linetype = "Recruitment max."
        ),
        color = "red",
        linewidth = 2
    ) +
    theme_bw() +
    theme(
        legend.position = "bottom",
        legend.box = "vertical",
        text = element_text(size = 18),
        axis.text.x = element_text(angle = 90, hjust = 1)
    )
timeline_plot
ggsave(
    fig_path("timeline_plot"),
    timeline_plot,
    width = 20,
    height = 12,
    dpi = 300
)
# }}}
```

### Clustering method

```{r}
# {{{
data <- fromJSON("../extraction.json")
# Printing only the text inside the square brackets:
methods <- gsub("\\].+", "", data$"clustering_method", perl = TRUE)
methods <- gsub("\\]", "", methods, perl = TRUE)
methods <- gsub("\\[", "", methods, perl = TRUE)
method_df <- data.frame(method = methods)
method_df$"method" <- gsub(" and ", " and \n", method_df$"method")
method_df$"method" <- str_to_sentence(method_df$"method")
method_plot <- method_df |>
    ggplot(
        aes(
            x = reorder(
                method,
                method,
                FUN = function(x) {
                    -1 * length(x)
                }
            )
        )
    ) +
    geom_bar() +
    scale_y_continuous(
        breaks = 0:13,
        minor_breaks = NULL
    ) +
    #labs(x = "Clustering method", y = "Number of studies") +
    labs(x = NULL, y = "Number of studies") +
    theme_bw() +
    theme(
        text = element_text(size = 14),
        axis.text.x = element_text(angle = 60, hjust = 1)
    )
ggsave(
    fig_path("method_plot"),
    method_plot,
    width = 7,
    height = 5,
    dpi = 300
)
# }}}
```

### Validation method

```{r}
# {{{
val_mat <- matrix(0, nrow = 30, ncol = 5)
val_methods <- data$"validation_method" |>
    lapply(
        function(y) {
            y |> lapply(
                function(x) {
                    val <- as.numeric(substr(x, 2, 2))
                    if (val > 0) val else NULL
                }
            ) |>
                unlist() |>
                unique()
        }
    )
for (i in seq_along(val_methods)) {
    methods <- val_methods[[i]]
    val_mat[i, methods] <- 1
}
rownames(val_mat) <- data$"clean_name"
colnames(val_mat) <- c(
    "Internal validation",
    "Separation on\nexternal features",
    "Stability to sample\nperturbation",
    "Stability to\nclustering methods",
    "Generalizes to\nexternal sample"
)
val_mat <- t(val_mat)
val_hm <- Heatmap(
    val_mat,
    row_names_side = "left",
    rect_gp = gpar(col = "black", lwd = 2),
    col = c("0" = "white", "1" = "orange"),
    show_column_dend = FALSE,
    cluster_rows = FALSE,
    heatmap_legend_param = list(
        title = "Method used",       # optional, overridden by custom Legend
        at = c("1"),
        labels = c("Yes")
    )
)

val_hm

pdf("figures/2026_04_01_val_method_hm.pdf", width = 9, height = 3.5)
draw(val_hm)
dev.off()
# }}}
```

### Summary

```{r}
# {{{
data <- fromJSON("../extraction.json")
options(width = 300)
cft_dfs <- lapply(
    seq_along(data$"study_id"),
    function(x) {
        df <- data$"clustering_features"[[x]]
        df$"study" <- data$"clean_name"[[x]]
        return(df)
    }
)
oft_dfs <- lapply(
    seq_along(data$"study_id"),
    function(x) {
        df <- data$"other_features"[[x]]
        df$"study" <- data$"clean_name"[[x]]
        return(df)
    }
)
cft_df <- do.call("rbind", cft_dfs)
oft_df <- do.call("rbind", oft_dfs[!data$"author" %in% c("lyons", "garcia")])
ft_df <- rbind(cft_df, oft_df)
multistudies <- ft_df |>
    dplyr::group_by(study) |>
    dplyr::summarize(n = max(solution)) |>
    dplyr::filter(n > 1) |>
    dplyr::pull(study)
# labeling for multiple cluster solutions within a study
# also treating the two Si et al. studies as coming from the same study
ft_df <- dplyr::mutate(
    ft_df,
    study_og = dplyr::case_when(
        study == "Si 2018a" ~ "Si 2018",
        study == "Si 2018b" ~ "Si 2018",
        TRUE ~ study
    ),
    solution = dplyr::case_when(
        study == "Si 2018b" ~ 2,
        TRUE ~ solution
    ),
    study = dplyr::case_when(
        study %in% multistudies ~ paste0(study, " (", solution, ")"),
        study == "Si 2018a" ~ "Si 2018 (1)",
        study == "Si 2018b" ~ "Si 2018 (2)",
        TRUE ~ study
    )
)

ft_df_sig <- ft_df |>
    dplyr::filter( !result %in% c("n.r.", "n.s."), goodness == TRUE) |>
    dplyr::select(-goodness, -report)

non_goodness_df <- ft_df |>
    dplyr::filter(
        !result %in% c("n.r.", "n.s."),
        tag %in% c("Female", "Non-White", "Age")
    ) |>
    dplyr::select(-goodness, -report)
non_goodness_df

ft_df_sig <- rbind(ft_df_sig, non_goodness_df)

twin_df <- ft_df |>
    dplyr::select(study_og, tag) |>
    dplyr::group_by(study_og, tag) |>
    dplyr::summarize(n = n()) |>
    dplyr::mutate(n = 1) |>
    as.data.frame() |>
    dplyr::group_by(tag) |>
    dplyr::summarize(n = dplyr::n()) |>
    arrange(n)
print(arrange(dplyr::filter(twin_df, n == 1), tag), n = Inf)
print(arrange(dplyr::filter(twin_df, n > 1), tag), n = Inf)

# This function takes a string like "1 > 7 > 5 > 3 = 6 > 2 > 4 > 8" 
# and calculates for each number a score based on the number of entities
# that number is greater than and less than.
parse_streak <- function(string) {
    # split on >
    groups <- strsplit(string, " > ")[[1]]
    # split further on =
    group_list <- lapply(groups, function(x) strsplit(x, " = ")[[1]])
    numbers <- sort(unique(unlist(group_list)))
    df <- data.frame(
        cluster = numbers,
        beats = integer(length(numbers)),
        loses_to = integer(length(numbers)),
        stringsAsFactors = FALSE
    )
    # iterate through and count win/loss tallies
    for (i in 1:length(group_list)) {
        for (j in 1:length(group_list)) {
            if (i != j) {
                for (a in group_list[[i]]) {
                    if (i < j) {
                        df$"beats"[df$"cluster" == a] <- df$"beats"[df$"cluster" == a] + length(group_list[[j]])
                    } else {
                        df$"loses_to"[df$"cluster" == a] <- df$"loses_to"[df$"cluster" == a] + length(group_list[[j]])
                    }
                }
            }
        }
    }
    df <- df |>
        dplyr::mutate(score = beats - loses_to) |>
        arrange(-score) |>
        dplyr::select(cluster, score)
    return(df)
}

parse_pairs <- function(string) {
    pairs <- strsplit(string, ";\\s*")[[1]]
    df <- data.frame()
    for (pair in pairs) {
        split <- strsplit(pair, " ")[[1]]
        if (split[[2]] == ">") {
            df <- rbind(
                df,
                data.frame(
                    cluster = c(split[[1]], split[[3]]),
                    score = c(1, -1)
                )
            )
        }
    }
    scored_df <- df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(score = sum(score)) |>
        data.frame()
    scored_df
}

# Input ranking string
test_streak_ranking <- "1 > 7 > 5 = 3 = 6 = 2 = 4 = 8"
test_pair_ranking <- "1 > 4; 2 > 4; 3 > 4; 2 > 1; 4 = 5"

parse_streak(test_streak_ranking)

overall_rank_within_set <- function(df) {
    # just pull all the results
    study_results <- df$"result"
    # parse all the results
    all_scores <- do.call(
        "rbind",
        lapply(
            study_results,
            function(x) {
                if (grepl(";", x)) {
                    parse_pairs(x)
                } else {
                    parse_streak(x)
                }
            }
        )
    )
    # assign overall ranks
    all_scores <- all_scores |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(score = sum(score))
    ranks <- dense_rank(-all_scores$"score")
    all_scores$"rank" <- ranks
    all_scores <- all_scores |>
        dplyr::arrange(rank)
    studies <- unique(df$"study")
    if (length(studies) == 1) {
        all_scores$"study" <- unique(df$"study")
    } else {
        stop("Data frame must only have 1 study")
    }
    all_scores
}

unique(ft_df_sig$"study")

overall_mappings <- lapply(
    unique(ft_df_sig$"study"),
    function(x) {
        study_df <- dplyr::filter(ft_df_sig, study == x)
        study_results <- study_df$"result"
        scaled_scores <- lapply(
                1:nrow(study_df),
                function(result_id) {
                    x <- study_results[[result_id]]
                    if (grepl(";", x)) {
                        parsed <- dplyr::mutate(
                            parse_pairs(x),
                            tag = study_df$"tag"[[result_id]],
                            score = score / max(abs(score))
                        )
                    } else {
                        parsed <- dplyr::mutate(parse_streak(x), tag = study_df$"tag"[[result_id]], 
                            score = score / max(abs(score))
                        )
                    }
                    if (all(is.na(parsed$"score"))) {
                        parsed$"score" <- 0
                    }
                    parsed
                }
            )
        all_scores <- do.call("rbind", scaled_scores)
        all_scores <- all_scores |>
            dplyr::group_by(cluster, tag) |>
            dplyr::summarize(score = sum(score)) |>
            data.frame() |> 
            group_by(tag) |>
            mutate(score = score / max(abs(score))) |>
            ungroup() |>
            data.frame() |>
            arrange(tag)
        all_scores_by_tag <- all_scores # save this
        all_scores_by_tag$"study" <- x
        all_scores <- all_scores |>
            dplyr::group_by(cluster) |>
            dplyr::summarize(score = sum(score))
        all_scores$"rank" <- dense_rank(-all_scores$"score")
        all_scores <- all_scores |>
            dplyr::arrange(rank)
        ranks <- all_scores$"rank"
        all_scores$"label" <- LETTERS[ranks]
        all_scores$"border" <- tibble(x = ranks) |>
            dplyr::group_by(x) |>
            mutate(n = row_number()) |>
            pull(n)
        all_scores$"study" <- x
        list("overall" = all_scores, "per_tag" = all_scores_by_tag)
    }
)

tag_only_ranks <- lapply(overall_mappings, function(x) x[[2]])
tag_only_ranks <- do.call("rbind", tag_only_ranks)
tag_only_ranks_tags <- unique(tag_only_ranks$"tag")
tag_only_ranks <- lapply(
    tag_only_ranks_tags,
    function(x) {
        my_df <- dplyr::filter(tag_only_ranks, tag == x)
        studies <- unique(my_df$"study")
        dfs <- lapply(
            studies,
            function(y) {
                tag_scores <- tibble(dplyr::filter(my_df, study == y))
                tag_scores$"rank" <- dense_rank(-tag_scores$"score")
                tag_scores <- arrange(tag_scores, rank)
                return(tag_scores)
            }
        )
        names(dfs) <- studies
        dfs
    }
)
names(tag_only_ranks) <- tag_only_ranks_tags

overall_mappings <- lapply(overall_mappings, function(x) x[[1]])

names(overall_mappings) <- unlist(
    lapply(overall_mappings, function(x) unique(x$"study"))
)

my_rect <- function(l, r, y, fill, border, line = 1) {
    rect(
      xleft   = l,
      xright  = r,
      ybottom = y - 0.3,
      ytop    = y + 0.3,  # height = 2
      col = fill,
      border = "#000000",
      lwd = line
    )
    if (border != "#000000") {
        points(
            x   = (l + r) / 2,
            y   = y,
            pch = 21,
            cex = 0.7,
            bg  = border,
            col = border
        )
    }
}

reset_canvas <- function(fts, studies, pad_bottom) {
    n_fts <- length(fts)
    n_studies <- length(studies)
    par(mar = c(pad_bottom, 8, 2, 2))  # bottom, left, top, right
    plot(
        0,
        0,
        type = "n",
        xlim = c(0, n_fts),
        ylim = c(0, n_studies + 1),
        xlab = "",
        ylab = "",
        yaxt = "n",
        xaxt = "n",
        xaxs = "i",
        yaxs = "i"
    )
    # grid lines
    x_grid <- c(1:100)
    y_grid <- seq(0.5, 100, by = 1)
    abline(v = x_grid, col = "gray80", lty = "solid", lwd = 1)
    # a vertical line to separate female / age
    abline(h = y_grid, col = "gray80", lty = "solid", lwd = 1)
    # x-axis
    axis(1, at = seq(0.5, n_fts, by = 1), labels = fts, las = 2)
    # y-axis
    axis(2, at = seq(1, n_studies, by = 1), labels = studies, las = 2)
    abline(v = 14, col = "black", lty = "solid", lwd = 2)
}
populate_column <- function(ranks, offset, study_names) {
    for (study_id in 1:length(study_names)) {
        study <- study_names[study_id]
        generate_rects(
            ranks[[study]],
            overall_mappings[[study]],
            y = study_id,
            x_offset = offset
        )
    }
}

draw_tie_bracket <- function(left,
                             right,
                             y,
                             gap,
                             x_offset,
                             y_offset = 0.47,
                             tick_height = 0.06) {
    segments(
        x0 = left  + gap / 2 + x_offset + 0.05,
        x1 = right - gap / 2 + x_offset - 0.05,
        y0 = y - 0.45,
        y1 = y - 0.45,
        lwd = 2
    )
}

generate_rects <- function(ft_ranks,
                           overall_map,
                           block_width = 0.95,
                           y = 1,
                           x_offset = 0,
                           gap = 0.025) {
    border_cols <- c("#000000", RColorBrewer::brewer.pal(7, name = "Accent"))
    if (!is.null(ft_ranks)) {
        n_colours <- length(unique(overall_map$label))
        palette <- colorRampPalette(c("white", "black"))(n_colours)
        overall_map$fill   <- palette[overall_map$rank]
        overall_map$border <- border_cols[overall_map$border]
        overall_fill <- dplyr::select(overall_map, rank, cluster, fill, border) |>
            dplyr::rename(overall_rank = rank)
        mapped_ranks <- dplyr::inner_join(ft_ranks, overall_fill, by = "cluster") |>
            dplyr::arrange(rank, overall_rank)
        n_rects <- length(mapped_ranks$cluster)
        if (n_rects > 0) {
            base_boundaries <- seq(0, block_width, length.out = n_rects + 1)
            x_offset <- x_offset + (1 - block_width) / 2
            lapply(seq_len(n_rects), function(i) {
                left  <- base_boundaries[i]   + gap / 2
                right <- base_boundaries[i+1] - gap / 2
                my_rect(
                    l = left  + x_offset,
                    r = right + x_offset,
                    y = y,
                    fill   = mapped_ranks$fill[i],
                    border = mapped_ranks$border[i]
                )
            })
            # Tie detection and bracket drawing
            ranks_vec <- mapped_ranks$rank
            tie_groups <- rle(ranks_vec)  # run-length encoding finds consecutive equal ranks
            idx <- 1
            for (g in seq_along(tie_groups$lengths)) {
                len <- tie_groups$lengths[g]
                if (len > 1) {  # only draw bracket for actual ties
                    i_start <- idx
                    i_end   <- idx + len - 1
                    grp_left  <- base_boundaries[i_start] + gap / 2
                    grp_right <- base_boundaries[i_end + 1] - gap / 2
                    draw_tie_bracket(
                        left     = grp_left,
                        right    = grp_right,
                        y        = y,
                        gap      = 0,      # already baked in above
                        x_offset = x_offset
                    )
                }
                idx <- idx + len
            }
            return(overall_map)
        }
    }
}
all_ranks_common <- tag_only_ranks[lapply(tag_only_ranks, length) > 5]
studies <- lapply(
    all_ranks_common,
    function(x) {
        names(x)
    }
) |>
    unlist() |>
    as.vector() |>
    unique()
cluster_compare_plot <- function(rank_data, studies, pad_bottom) {
    reset_canvas(
        fts = names(rank_data),
        studies = studies,
        pad_bottom
    )
    for (x in seq_along(rank_data)) {
        populate_column(rank_data[[x]], x - 1, studies)
    }
}
# We can put a number to how well sorted each feature is by spearman correlations
calc_spearman <- function(study, feature) {
    global <- overall_mappings[[study]]
    local <- all_ranks_common[[feature]][[study]]
    if (is.null(global) | is.null(local)) {
        return(NA)
    }
    global <- global |>
        dplyr::rename("global_rank" = "rank") |>
        dplyr::select(-study, -score)
    local <- local |> 
        dplyr::rename("local_rank" = "rank") |>
        dplyr::select(-study, -score)
    joined <- dplyr::full_join(global, local, by = "cluster")
    correlation <- cor(joined$"global_rank", joined$"local_rank")
    return(correlation)
}
res <- outer(
    studies,
    names(all_ranks_common),
    Vectorize(calc_spearman)
)
# Collapse correlations across studies first
res_df <- data.frame(res)
res_df$"study" <- studies
study_table <- ft_df |>
    dplyr::select(study, study_og) |>
    dplyr::group_by(study, study_og) |>
    dplyr::summarize(n = dplyr::n()) |>
    dplyr::select(-n)
res_df <- dplyr::inner_join(
    res_df,
    study_table,
    by = "study"
)
colnames(res_df) <- c(names(all_ranks_common), "study", "study_og")
res_corrs <- res_df |>
    group_by(study_og) |>
    summarise(
        across(where(is.numeric), ~ mean(.x, na.rm = TRUE)),
        .groups = "drop"
    ) |>
    dplyr::select(-study_og) |>
    colMeans(na.rm = TRUE)

dimnames(res) <- list(studies, names(all_ranks_common))
sorted_tags <- names(sort(res_corrs, decreasing = TRUE))
sorted_ranks <- all_ranks_common[sorted_tags]
nums <- colMeans(res, na.rm = TRUE) |>
    sort(decreasing = TRUE) |>
    round(2)
sorted_names <- paste0(names(all_ranks_common[sorted_tags]), "\n(", nums, ")")
names(sorted_ranks) <- sorted_names

# Chan, Bui, Si 2018 (1 and 2) and Simons 2024
res_df |>
    data.frame() |>
    dplyr::filter(Female > 0) |>
    dplyr::select(study, Female)

# Blundell, Kinney, MacGregor
res_df |>
    data.frame() |>
    dplyr::filter(Female < 0) |>
    dplyr::select(study)
```

```{r}
png(fig_path("cluster_summary_plot"), width = 2000, height = 1400, res = 150)
cluster_compare_plot(sorted_ranks, sort(studies), pad_bottom = 9)
dev.off()
# }}}
```

### journals

```{r}
years <- data.frame(
    journal = data$"journal",
    year = data$"year"
)

years

ifs <- data.frame(
    journal = unique(data$"journal"),
    impact = c(2, 9.7, 3.3, 7.7, 3.4, 1.8, 9.0, 2.5, 3.8, 2.1, 16.3, 1.9,
        3.0, 2.6, 3.7, 2.6, 2.7, 4.5)
)

journals <- dplyr::full_join(
    years, ifs
)

jlevels_year <- journals |>
    group_by(journal) |>
    #dplyr::summarize(sort_val = dplyr::n()) |>
    dplyr::summarize(sort_val = max(year)) |>
    arrange(sort_val) |>
    pull(journal)

jlevels_freq <- journals |>
    group_by(journal) |>
    dplyr::summarize(sort_val = dplyr::n()) |>
    arrange(sort_val) |>
    pull(journal)

jlevels_if <- journals |>
    group_by(journal) |>
    #dplyr::summarize(sort_val = dplyr::n()) |>
    dplyr::summarize(sort_val = max(impact)) |>
    arrange(sort_val) |>
    pull(journal)


journals$"journal_year" <- factor(journals$"journal", levels = jlevels_year)
journals$"journal_freq" <- factor(journals$"journal", levels = jlevels_freq)
journals$"journal_if" <- factor(journals$"journal", levels = jlevels_if)

journals

p1 <- journals |>
    ggplot(
        aes(x = year, y = journal_freq, colour = log(impact))
    ) +
    geom_hline(yintercept = 13.5, color = "red") +
    geom_point(aes(size = log(impact))) +
    xlim(c(2012, 2025)) +
    theme_bw() +
    theme(text = element_text(size = 14))
p2 <- journals |>
    ggplot(
        aes(x = year, y = journal_year, colour = log(impact))
    ) +
    geom_hline(yintercept = 13.5, color = "red") +
    geom_point(aes(size = log(impact))) +
    xlim(c(2012, 2025)) +
    theme_bw() +
    theme(text = element_text(size = 14))
p3 <- journals |>
    ggplot(
        aes(x = year, y = journal_if, colour = log(impact))
    ) +
    geom_point(aes(size = log(impact))) +
    geom_hline(yintercept = 13.5, color = "red") +
    xlim(c(2012, 2025)) +
    theme_bw() +
    theme(text = element_text(size = 14))
full_plot <- patchwork::wrap_plots(c(p1, p2, p3), ncol = 1)
ggsave("figures/journal_plot.png", full_plot, width = 12, height = 12)
```

Journals that come up include:

- from frequency
    - the journal of head trauma rehabilitation
    - brain injury
    - archives of clinical neuropsychology
    - neuropsychology
    - journal of neurotrauma
- from recency
    - plos digital health
    - disability and rehabilitation
    - the journal of head trauma rehabilitation
    - the american journal of sports medicine
    - journal of women's health
- from if
    - british journal of sports medicine
    - jama network open
    - neurology
    - plos digital health
    - the american journal of sports medicine

The study is not seem all that suitable for a sports journal or neurology journal. 
And does not quite seem at the caliber of jama network open.
So that leaves:

1. plos digital health
2. journal of neurotrauma
3. the journal of head trauma rehabilitation
4. neuropsychology
5. archives of clinical neuropsychology
6. disability and rehabilitation
7. journal of women's health
8. brain injury

Starting with PLOS digital health also has the perk of there being no restrictions on length / figures / tables.

lab meeting?

mention sex and its covariates probably are covaried with sex,


